\documentclass[11pt,a4paper,sans]{moderncv}

% ----------------------------------------------------------------------------------
%            Basic Settings & Packages
% ----------------------------------------------------------------------------------
% Adjust page margins
\usepackage[scale=0.75]{geometry}

% Font encoding (Compile with XeLaTeX)
\usepackage{fontspec}

% Icon packages
\usepackage{fontawesome5}
\usepackage{academicons}

% ModernCV theme and colors
\moderncvstyle{classic} 
\moderncvcolor{blue}
\setlength{\hintscolumnwidth}{3cm}

% ----------------------------------------------------------------------------------
%            Personal Information
% ----------------------------------------------------------------------------------
% Font adjustment
\renewcommand*{\namefont}{\Huge\mdseries\upshape}

% Name and Title
\name{Zhixing}{You}
\title{Postdoctoral Researcher} 

% Address: Institution on first line (bold), campus/city on second line
\address{\textbf{Einstein Institute of Mathematics}}{The Hebrew University of Jerusalem, Edmond J. Safra Campus}

% Contact info
\phone[mobile]{+86~188~1011~8552}
\email{zhixing.you@mail.huji.ac.il}

% Extra Info (Google Scholar)
\extrainfo{%
    \centering 
    \aiGoogleScholar\ \href{https://scholar.google.com/citations?user=B_DTCdcAAAAJ}{Google Scholar}%
}

% ----------------------------------------------------------------------------------
%            Document Content
% ----------------------------------------------------------------------------------
\begin{document}

\makecvtitle

% ----------------------------------------------------------------------------------
%            Work Experience
% ----------------------------------------------------------------------------------
\section{Work Experience}
\cventry{Oct 2025 -- Present}
{Postdoctoral Researcher}
{Einstein Institute of Mathematics, The Hebrew University of Jerusalem}
{Israel}
{Advisor: Yair Hayut}
{}

\cventry{Jul 2022 -- Sep 2025}
{Postdoctoral Researcher}
{Department of Mathematics, Bar-Ilan University}
{Israel}
{Advisor: Assaf Rinot}
{}

% ----------------------------------------------------------------------------------
%            Education
% ----------------------------------------------------------------------------------
\section{Education}
\cventry{Sep 2016 -- Jun 2022}
{Ph.D. in Basic Mathematics}
{Academy of Mathematics and Systems Science, Chinese Academy of Sciences}
{Beijing, China}
{Advisors: Joan Bagaria, Liuzhen Wu, Jiachen Yuan}
{}

\cventry{Oct 2020 -- Dec 2021}
{Joint Ph.D. Program in Mathematics}
{University of Barcelona}
{Spain}
{Funding: China Scholarship Council (CSC)}
{}

\cventry{Sep 2012 -- Jul 2016}
{B.Sc. in Mathematics and Biology}
{Nankai University}
{Tianjin, China}
{}
{}

% ----------------------------------------------------------------------------------
%            Selected Publications
% ----------------------------------------------------------------------------------
\section{Selected Publications}

\cvitem{[1]}{\textbf{Indecomposable cardinals} (with Jiachen Yuan), preprint.}

\cvitem{[2]}{\textbf{A new model in which all C-sequences are trivial} (with Assaf Rinot and Jiachen Yuan), \emph{Journal of Symbolic Logic}, published online 2026. DOI: \url{https://doi.org/10.1017/jsl.2026.10183}}

\cvitem{[3]}{\textbf{Ketonen’s question and other cardinal sins} (with Assaf Rinot and Jiachen Yuan), \emph{Israel Journal of Mathematics} (Accepted), preprint: \url{https://arxiv.org/abs/2408.01547}}

\cvitem{[4]}{\textbf{The vanishing levels of a tree} (with Assaf Rinot and Shira Yadai), \emph{Canadian Journal of Mathematics}, published online 2025. DOI: \url{https://doi.org/10.4153/S0008414X2510148X}}

\cvitem{[5]}{\textbf{How far is almost strong compactness from strong compactness} (with Jiachen Yuan), \emph{Journal of Mathematical Logic}, 2025. DOI: \url{https://doi.org/10.1142/S0219061324500090}}

\cvitem{[6]}{\textbf{Full Souslin trees at small cardinals} (with Assaf Rinot and Shira Yadai), \emph{Journal of the London Mathematical Society}, 2024. DOI: \url{https://doi.org/10.1112/jlms.12957}}

\cvitem{[7]}{\textbf{On the cofinality of the least $\lambda$-strongly compact cardinal} (with Jiachen Yuan), \emph{Journal of Symbolic Logic}, 2024. DOI: \url{https://doi.org/10.1017/jsl.2023.4}}

% ----------------------------------------------------------------------------------
%            Academic Services
% ----------------------------------------------------------------------------------
\section{Academic Services}
\cvitem{Reviewer}{Archive for Mathematical Logic}

% ----------------------------------------------------------------------------------
%            Academic Talks
% ----------------------------------------------------------------------------------
\section{Academic Talks}
\cvitem{[1]}{Indeterminacy of longer Welch game. \emph{Set Theory Seminar in Jerusalem}, Hebrew University of Jerusalem, Israel, Feb 2026.}

\cvitem{[2]}{Controlling the strength of some large cardinals that carry an indecomposable ultrafilter. \emph{Set Theory Seminar in Jerusalem}, Hebrew University of Jerusalem, Israel, Nov 2025.}

\cvitem{[3]}{The intersection of a sequence of outer models and sum ultrafilter constructions. \emph{Set Theory Seminar in Jerusalem}, Hebrew University of Jerusalem, Israel, May 2024.}

\cvitem{[4]}{Intersection of a sequence of outer models. \emph{Bar-Ilan University Set Theory Seminar}, Bar-Ilan University, Israel, May 2024.}

\cvitem{[5]}{Adding entangled branches to a $\kappa$-Suslin tree. \emph{Institute of Mathematics Set Theory Seminar}, Chinese Academy of Sciences, Nov 2023.}

\cvitem{[6]}{The vanishing level of a tree. \emph{2023 Chinese Annual Conference on Mathematical Logic}, Sun Yat-sen University, Nov 2023.}

\cvitem{[7]}{Some new constructions of Suslin trees. \emph{Mathematical Logic Seminar}, Wuhan University, Oct 2023.}

\cvitem{[8]}{How far is almost strong compactness from strong compactness. \emph{Logic Colloquium 2023}, University of Milan, Italy, Jun 2023.}

\cvitem{[9]}{Identity crisis between $\delta$-strongly compact cardinals. \emph{Tel Aviv University Set Theory Seminar}, Tel Aviv University, Israel, Sep 2022.}

\cvitem{[10]}{Hierarchies of $\delta$-strongly compact cardinal. \emph{Annual meeting of The Israel Mathematical Union}, Ben Gurion University of the Negev, Israel, Sep 2022.}

\cvitem{[11]}{A minimal Magidor-type forcing (countable case). \emph{Bar-Ilan University Set Theory Seminar}, Bar-Ilan University, Israel, Sep 2022.}

\cvitem{[12]}{On the $\delta$-strongly compact cardinal. \emph{Bar-Ilan University Set Theory Seminar}, Bar-Ilan University, Israel, Aug 2022.}

\cvitem{[13]}{Strong compactness and its variation. \emph{Mathematical Logic Seminar}, Wuhan University, Mar 2022.}

\cvitem{[14]}{Hierarchies of $\delta$-strongly but not full strongly compact cardinals. \emph{Barcelona Set Theory Seminar}, University of Barcelona, Spain, Sep 2021.}

\cvitem{[15]}{Hierarchies of $\delta$-strongly but not full strongly compact cardinals. \emph{Logic Workshop in Nanjing}, Nanjing University, Mar 2021.}

\cvitem{[16]}{Minimal Magidor-type forcing (Countable case). \emph{Prikry Forcing Online}, University of East Anglia, Dec 2020.}

\end{document}